analysis

### 2024-12-04 analysis.qmd
jw_push for mlr

```{r}
combined <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/combined.csv')
```

@@

```{r}
combined <- combined |> mutate(State_fac = factor(combined$State), Region_fac = factor(combined$Region, levels=c('South', 'West', 'Northeast', 'Midwest'), labels=c(0, 1, 2, 3)))
```

@@

```{r}

library(mice)
library(sjlabelled)
library(tidyverse)

@@

```{r}
#Need to convert school funding adequacy imputed values to school funding categorical variable before using in models
```

```{r}
#MLR
#Outcome = life expectancy
#Predictors = residential segregation, limited access to healthy foods, uninsured adults, region_fac as interaction with residential segregation (or any other variable)
```

@@

```{r}
#Logistic 
#Outcome = School.Funding.Cat
#Predictors = residential segregation, median.household.income, median.prop.tax
```

>>>>

```{r, echo= FALSE}
library("dplyr")
library(mice)
library(sjlabelled)
library(tidyverse)

combined <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/combined.csv')
```

@@

```{r}
combined <- combined |> mutate(State_fac = factor(combined$State), Region_fac = factor(combined$Region, levels=c('South', 'West', 'Northeast', 'Midwest')))
```

@@

```{r}
#Need to convert school funding adequacy imputed values to school funding categorical variable before using in models
# imputated data has 5 dataframes within a list, need to run a loop for all five datasets to create a categorical variable for each set. 
```

```{r}
#MLR
# Outcome = life expectancy #Predictors = residential segregation, limited access to healthy foods, uninsured adults, region_fac as interaction with residential segregation (or any other variable)

mlrmodel <- lm(
  Life.Expectancy ~ Residential.Segregation.Index +
    X..Limited.Access.to.Healthy.Foods +
    X..Uninsured.Adults,
  data = combined)
summary(mlrmodel)

@@

```{r}
mlr.imp.mod <- with(sub.imp, lm(Life.Expectancy ~ Residential.Segregation.Index +
    X..Limited.Access.to.Healthy.Foods +
    X..Uninsured.Adults + 
    Region_fac))

summary(pool(mlr.imp.mod))
```

```{r}
mlr.imp.mod2 <- with(sub.imp, lm(Life.Expectancy ~ Residential.Segregation.Index +
    X..Limited.Access.to.Healthy.Foods +
    X..Uninsured.Adults + 
    Region_fac + 
    Region_fac * Residential.Segregation.Index))

summary(pool(mlr.imp.mod2))
```

@ UZO: Add plots to check assumptions: QQ plot, nested F-test, write p-value interpretations, VIF, Cooks distance

@@

```{r}
#Logistic 
lmod <- glm(School.Funding.Cat ~ Residential.Segregation.Index + Median.Household.Income + Median.Prop.Tax,
              data=combined,
              family="binomial")
summary(lmod)

with(sub.imp, glm(School.Funding.Cat ~ Residential.Segregation.Index + Median.Household.Income + Median.Prop.Tax, family="binomial"))

#Outcome = School.Funding.Cat
#Predictors = residential segregation, median.household.income, median.prop.tax
```
